\chapter*{Acknowledgements}
% 
This thesis would not have been possible without the help of different people. I
would like to thank Dorothea Wagner for giving me the opportunity to work in her
group and to take care of the funding. During that time I was part in different
projects such as the Helmholtz Program Storage and Cross-linked Infrastructure
(SCI), Energy System Integration (ESI), and as an associate in the GRK Energy
Status Data, where I learned a lot. In addition, I would like to thank my
reviewers Sylvie Thi\'ebaux and Dorothea Wagner for their comments and their
advises.

Working on such a complex topic alone would have been impossible and thus, I
would like to thank my coauthors Alban Grastien, Sebastian Lehmann, Thomas
Leibfried, Tamara Mchedlidze, Nico Meyer-Hübner, Martin Nöllenburg, Ignaz
Rutter, Peter Sanders, Dorothea Wagner, and Matthias Wolf for their discussions
and collaboration. I owe a big thanks to Andreas Gemsa, Sascha Gritzbach,
Matthias Wolf, and Philipp Bohnenstengel who proofread parts of my thesis. A
special thanks goes to Philipp, who read the whole thesis and fixed my ``-ly'',
and ``analysis'' problems, and found the ``conjured complex'' to be a bit
magical.

To get a broader knowledge, I was lucky to work on other topics, collaborate
with other groups, and learn from different colleagues. A special thanks here
goes to Moritz Baum from whom I learned how to collaborate on a paper and who
gave me very good advises. In addition, I would like to thank for the numerous
colleagues Moritz Baum, Thomas Bl\"asius, Johannes Garttner, Andreas Gemsa,
Sascha Gritzbach, S\"oren Hohmann, Heiko Maa{\ss}, Carina Mieth, Martin Pfeifer,
Ignaz Rutter, Philipp Staudt, Torsten Ueckerdt, Dorothea Wagner, Christof
Weinhardt, and Matthias Wolf with whom I was allowed to work together on
different papers in external projects.

Research is one thing, but we have also the responsibility to communicate our
knowledge in a better and more understandable way. I was very lucky to work with
Anna Caroline Hein on an article that describes our work in a more accessible
way. She taught me how to write an article for non-specialists and what are
common tools to spread our knowledge.

I thank the colleagues at~\gls{nicta} for the very good working atmosphere. I
learned a lot from the team about electrical flows and optimization. Major parts
of the switching paper were developed during that time and afterwards with
Matthias Wolf, from whom I learned theoretical techniques and who is a kind 
reviewer of my writings. Furthermore, I thank also my colleagues at the
institute from whom I learned a lot in algorithmics and theoretical computer
science. Especially, I would like to thank Spyros Kontogiannis, who was my first
temporary office mate in the ``exile'' office, and my office mates Benjamin
Niedermann and Matthias Wolf with whom I enjoyed the daily vending machine trips
and ``apple walks'' a lot. In addition, I recall the times with most of my
coworkers when we spent long nights at the institute, the Dibbelt ghost and its
hectic squeak of shoe soles, the weekends at work with the Italian course at the
Pizzahaus and the pizza ``Quattro Fromage'', the Saboteur counterpart, the
members of the Escorial committee, the Obstfreunde meetings, the soccer games
after work, the legendary ``Frauenwasserballweltmeisterschaft'' in Gernsbach,
and the illegal office chair race. I would like to thank especially these
colleagues that made long or bad days enjoyable.

There are people in the background that help out with all the administration and
technical belongings, which helped me to focus on my main work. This part was
perfectly done by Lilian Becker, Isabelle Junge, Ralf K\"olmel, Laurette
Lauffer, and Tanja Wehrmann, whom I would particularly like to thank.

Starting a thesis template from scratch would take a lot of time. I inherited
the template and improvements from Thomas Bl\"asius and Moritz Baum,
respectively. I would like to thank both, since it was super easy to add
additional fixes and ideas to the template.

In the end, I would like to thank my friends, my family, dedicated teachers
(especially Eva Pudewell and Jana Schreiber), inspiring research staff such as
Ingo Boersch that invested time for students from school, and all people who
brought me back on track and supported me over all this years. A special thanks
goes to Katja and Marius Rothe, Philipp Bohnenstengel, Moritz Baum, Anna
Caroline Hein, Andreas Gemsa, Thomas Bl\"asius, Benjamin Niedermann, and Cliff
M\"andl, who supported me mentally and emotionally very much.
% 