%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Problems %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Wind Farm
\newglossaryentry{fffp}
{
    name={\wfffp},
    longform={flexible full farm problem},
    capitalform={\WfFFP},
    sort={fffp},
    % type={windfarmmodel},
    % 
    description={The~\glslongform{fffp} represents the cabling of multiple
    collector systems with substation locations. In this problem layer the
    location of the substation is not fix and has to be computed, too. Note that
    the assignment of turbines is neither fixed to a circuit nor to a
    substation. The~\glslongform{sp} and~\glslongform{cp} are subproblems.
    See~\cref{ch:wfcp:fig:topological-description} for more information.},
    % 
    symbol={\wfffp}
}

\newglossaryentry{cp}
{
    name={\wcp},
    longform={\textsc{Circuit Problem}\xspace},
    capitalform={\WCP},
    sort={wfcp2Cp},
    parent={fffp},
    % type={windfarmmodel},
    description={\glscapitalform{cp} (\gls{cp}) is the smallest problem layer in
    the wind farm layout problem hierarchy. In this problem layer only the cable
    layout of a circuit---a connected component connected to a substation---is
    considered, where turbines are either connected to other turbines or to a
    preassigned substation. See~\cref{ch:wfcp:fig:topological-description} for
    more information.}, symbol={\wcp} }

\newglossaryentry{circuit}
{
    name={circuit},
    longform={circuit},
    capitalform={Circuit},
    sort={circuit},
    % type={windfarmmodel},
    description={The term~\emph{circuit} can have different meanings. In terms
    of bases it represents a simple cycle and in terms of wind farm cabling it
    represent one connected component that is assigned to a substation 
    (see~\cref{ch:wfcp:fig:topological-description}).},
    % 
    symbol={circuit} }

\newglossaryentry{collectorSystem}
{
    name={collector system},
    longform={collector system},
    capitalform={Collector System},
    sort={wfcp3CollectorSystem},
    parent={fffp},
    % type={windfarmmodel},
    % 
    description={The~\glslongform{collectorSystem} is a part of a wind farm,
    where multiple circuits are connected to one substation.
    A~\glslongform{collectorSystem} has a preassigned substation. }, 
    % 
    symbol={collector system} 
}

\newglossaryentry{sp}
{
    name={\wsp},
    longform={\textsc{Substation Problem}\xspace},
    capitalform={\WSP},
    sort={wfcp1Sp},
    parent={fffp},
    % 
    description={The~\glslongform{sp} is a cabling of multiple independent
    circuits with one preassigned substation. This represents the cable layout
    of a single collector system of a substation in the wind farm. Note that the
    turbines are not assigned to a circuit. Thus, the~\glslongform{cp} can be
    seen as a subproblem if the turbine to substation assignment is computed. 
    See~\cref{ch:wfcp:fig:topological-description} for more information.},
    % 
    symbol={\wsp}
}

\newglossaryentry{ffp}
{
    name={\wffp},
    longform={\textsc{Full Farm Problem}\xspace},
    capitalform={\WFFP},
    sort={wfcp0Ffp},
    parent={fffp},
    % 
    description={The~\glslongform{ffp} represents the cabling of multiple
    collector systems with fix substation locations. Note that the assignment of
    turbines is neither fixed to a circuit nor to a substation.
    The~\glslongform{sp} and~\glslongform{cp} are subproblems.
    See~\cref{ch:wfcp:fig:topological-description} for more information.},
    % 
    symbol={\wffp}
}

\newglossaryentry{pcc}
{
    name={PCC},
    longform={point of common connection},
    capitalform={Point of Common Connection},
    sort={pcc},
    % 
    description={The Point of Common Connection (\glssymbol{pcc}) represents the
    on-shore connection point to the mainland power grid. See~\cref{ch:wfcp:fig:topological-description} for more information.},
    % 
    symbol={PCC}
}

\newglossaryentry{temperature}
{
    name={\ensuremath{\temperature}},
    longform={temperature},
    capitalform={Temperature},
    sort={wfcpTemperature},
    type={model},
    % 
    description={The cooling schedule is a non-increasing monotone
    function~$\glssymbol{temperature}\colon\naturals\to (0,\infty)$, where~$
    \glssymbol{temperature}(\glssymbol{timestamp})$ is the temperature at
    time~\glssymbol{timestamp}. },
    % 
    symbol={\ensuremath{\temperature}}
}


% turbines and substations
% 
\newglossaryentry{instances}
{
    name={\ensuremath{\instances}},
    longform={instances},
    capitalform={Instances},
    sort={wfcpInstances},
    type={model},
    % 
    description={
        The set of instances~\glssymbol{instances}, where each
        instance~$\glssymbol{instance}\in\glssymbol{instances}$ is a
        tuple~$\instancec = (
        \glssymbol{solution}_{\glssymbol{timestamp}},
        \glssymbol{bestsolution},
        \glssymbol{temperature},
        \glssymbol{thermalConductivityCapacity},
        \glssymbol{activity})$.
    },
    % 
    symbol={\ensuremath{\instances}}
}

\newglossaryentry{instance}
{
    name={\ensuremath{\instance}},
    longform={instance},
    capitalform={instance},
    sort={wfcpInstance},
    parent={instances},
    type={model},
    % 
    description={An instance~$\glssymbol{instance}\in\glssymbol{instances}$ is a
        tuple~$\instancec = (
        \glssymbol{solution}_{\glssymbol{timestamp}},
        \glssymbol{bestsolution},
        \glssymbol{temperature},
        \glssymbol{thermalConductivityCapacity},
        \glssymbol{activity})$.
    },
    % 
    symbol={\ensuremath{\instance}}
}

\newglossaryentry{energy}
{
    name={\ensuremath{\Delta\energy}},
    longform={energy},
    capitalform={Energy},
    sort={wfcpEnergy},
    type={model},
    % 
    description={ The cost difference (or energy) of two solutions~\solutiona
        and~\solutionb is computed by~$
        \glssymbol{energy}
        =
        \glssymbol{windfarmTotalcost}(\glssymbol{solution}_{\glssymbol{timestamp}+1})
        -
        \glssymbol{windfarmTotalcost}(\glssymbol{solution}_{\glssymbol{timestamp}})
        $. 
    },
    % 
    symbol={\ensuremath{\Delta\energy}}
}

\newglossaryentry{cabletypes}
{
    name={\ensuremath{\cabletypes}},
    longform={cabletypes},
    capitalform={Cabletypes},
    sort={wfcpCabletypes},
    type={model},
    % 
    description={The set of cable types is denoted by~\glssymbol{cabletypes}.
    See~\glslongform{cabletype}~\glssymbol{cabletype} for a detailed
    specification of a cable type and for an example set of cable types
    see~\cref{ch:wfcp:tbl:fig:cabletypes}.},
    % 
    symbol={\ensuremath{\cabletypes}}
}

\newglossaryentry{cabletype}
{
    name={\ensuremath{\cabletype}},
    longform={cabletype},
    capitalform={cabletype},
    sort={wfcpCabletype},
    parent={cabletypes},
    type={model},
    % 
    description={A~\glslongform{cabletype} is denoted by~\glssymbol{cabletype}.
    Each cable type has a thermal limit~\glssymbol{capacity} and a cost per
    unit~\glssymbol{windfarmCableCost}, where the unit can be meter~\si{\metre}.
    See for example~\cref{ch:wfcp:tbl:fig:cabletypes}.
    },
    % 
    symbol={\ensuremath{\cabletype}}
}

\newglossaryentry{probability}
{
    name={\ensuremath{\probability}},
    longform={probability},
    capitalform={Probability},
    sort={wfcpProbability},
    type={model},
    % 
    description={ The probability~$\glssymbol{probability}\in\posreals$ and
        describes the probability of accepting a worse solution~$\solutionb$
        from~$\solutiona$ and is designed in such a way that probability of the
        acceptance of worse solutions is in the beginning higher and deceases
        over the time. All possible probabilities are assumed to
        be~$\sum_{\solutionb\in\glssymbol{solutions}
        (\solutiona)}\glssymbol{probability}_{
        \solutiona\solutionb}=1$.
    },
    % 
    symbol={\ensuremath{\probability}}
}

\newglossaryentry{solutions}
{
    name={\ensuremath{\solutions}},
    longform={solutions},
    capitalform={solutions},
    sort={wfcpSolutions},
    type={model},
    % 
    description={The set of solution is denoted by~\glssymbol{solutions}.
    % 
    We also define the neighborhood of solutions, where we denote that
    solution~$\solutiona$ is neighbor of solution~$\solutionb$
    by~$\solutiona\in\glssymbol{solutions}(\solutionb)$. This holds only if and
    only if~$\solutionb\in\glssymbol{solutions}(\solutiona)$.},
    % 
    symbol={\ensuremath{\solutions}}
}

\newglossaryentry{solution}
{
    name={\ensuremath{\solution}},
    longform={solution},
    capitalform={Solution},
    sort={wfcpSolution},
    parent={solutions},
    type={model},
    % 
    description={ A solution at time~\mbox{$\glssymbol{timestamp}\in\naturals$}
    is denoted
    by~$\glssymbol{solution}_{\glssymbol{timestamp}}\in\glssymbol{solutions}$,
    where each solution is a
    tupel~$\glssymbol{solution}_{\glssymbol{timestamp}}=(\glssymbol{network}^{\glssymbol{timestamp}},
    \glssymbol{flow})$
    with a flow network~\glssymbol{network} at time~$\glssymbol{timestamp}$, where
    the underlying graph~\glssymbol{graph} changes dependent on~$\glssymbol{timestamp}$ denoted
    by~$\glssymbol{graph}^{\glssymbol{timestamp}}=(
    \glssymbol{edges}^{\glssymbol{timestamp}}\subseteq\glssymbol{edges},\glssymbol{vertices})$.
    },
    % 
    symbol={\ensuremath{\solution}}
}

\newglossaryentry{bestsolution}
{
    name={\ensuremath{\bestsolution}},
    longform={bestsolution},
    capitalform={Best Solution},
    sort={wfcpInstances},
    parent={solutions},
    type={model},
    % 
    description={The best feasible solution found so far is denoted
    by~\glssymbol{bestsolution}.},
    % 
    symbol={\ensuremath{\bestsolution}}
}

\newglossaryentry{activity}
{
    name={\ensuremath{\activity}},
    longform={activity},
    capitalform={Activity},
    sort={wfcpActivity},
    type={model},
    % 
    description={The activity~\glssymbol{activity} is defined
    in~\cref{ch:wfcp:sa:eq:dynamic-cooling-schedule} and is used for the dynamic
    cooling schedule as an adjustment factor for the cooling curve. The cooling
    schedule is adjusted to different network sizes using the activity. },
    % 
    symbol={\ensuremath{\activity}}
}

\newglossaryentry{representations}
{
    name={\ensuremath{\representations}},
    longform={representations},
    capitalform={Representations},
    sort={wfcpRepresentations},
    type={model},
    % 
    description={The representation~\glssymbol{representations} is a
    tuple~$\glssymbol{representations}=(\glssymbol{potential},
    \glssymbol{cuts})$, where~\glssymbol{potential} is permutation function
    and~\glssymbol{cuts} is cut set.
    },
    % 
    symbol={\ensuremath{\representations}}
}

\newglossaryentry{potential}
{
    name={\ensuremath{\potential}},
    longform={potential},
    capitalform={potential},
    sort={wfcpPotential},
    type={model},
    % 
    description={The potential field is defined by a permutation
    function~$\glssymbol{potential}\colon\glssymbol{vertices}\to\glssymbol{vertices}$.
    },
    % 
    symbol={\ensuremath{\potential}}
}

\newglossaryentry{partition}
{
    name={\ensuremath{\partition}},
    longform={partition},
    capitalform={partition},
    sort={wfcpPartition},
    type={model},
    % 
    description={A partition is a subset of the set of vertices, \eg, a subset
    of a set of substation is denoted by~$\glssymbol{partition}\subsetneq
    \glssymbol{consumers}$.
    },
    % 
    symbol={\ensuremath{\partition}}
}

\newglossaryentry{possiblesubstations}
{
    name={\ensuremath{\possiblesubstations}},
    longform={possiblesubstations},
    capitalform={possiblesubstations},
    sort={wfcpPossiblesubstations},
    type={model},
    % 
    description={The set of possible substation position is denoted
    by~\glssymbol{possiblesubstations}. It is used in the~\glslongform{fffp}
    (\gls{fffp}), where the position of a set of
    substations~\glssymbol{consumers} is not fixed. },
    % 
    symbol={\ensuremath{\possiblesubstations}}
}

\newglossaryentry{len}
{
    name={\ensuremath{\len}},
    longform={len},
    capitalform={len},
    sort={wfcpLen},
    type={model},
    % 
    description={ A edge weight
    function~\mbox{$\glssymbol{len}\colon\glssymbol{edges}\to\posreals$} that
    represents the length of a cable. },
    % 
    symbol={\ensuremath{\len}}
}

\newglossaryentry{capacityTightness}
{
    name={\ensuremath{\capacityTightness}},
    longform={capacityTightness},
    capitalform={capacityTightness},
    sort={wfcpCapacityTightness},
    type={model},
    % 
    description={The substation capacities are characterized by the
    \emph{substation capacity tightness}~$\glssymbol{capacityTightness}$ that
    measures the the ratio of maximum supply and maximum demand. We call this
    ratio tight if~$\glssymbol{capacityTightness}=1$.},
    % 
    symbol={\ensuremath{\capacityTightness}}
}

\newglossaryentry{substationCapacityVariance}
{
    name={\ensuremath{\substationCapacityVariance}},
    longform={substationCapacityVariance},
    capitalform={substationCapacityVariance},
    sort={wfcpSubstationCapacityVariance},
    type={model},
    % 
    description={ The substation capacity
    variance~$\glssymbol{substationCapacityVariance}$ restricts the net flow
    interval at a substation (see~\cref{ch:wfcp:generator:eq:delta}). },
    % 
    symbol={\substationCapacityVariance}
}

\newglossaryentry{shapeAspectRatio}
{
    name={\shapeAspectRatio},
    longform={shapeAspectRatio},
    capitalform={shapeAspectRatio},
    sort={wfcpShapeAspectRatio},
    type={model},
    % 
    description={ The wind farm shape of the benchmark sets
    (\cref{ch:wfcp:sec:benchmark-generator}) is defined by an ellipse that is
    described by the aspect ratio~$\glssymbol{shapeAspectRatio}\in(0,1]$.  },
    % 
    symbol={\shapeAspectRatio}
}

\newglossaryentry{kNearestNeighbor}
{
    name={\kNearestNeighbor},
    longform={kNearestNeighbor},
    capitalform={kNearestNeighbor},
    sort={wfcpKNearestNeighbor},
    type={model},
    % 
    description={The~$\glssymbol{kNearestNeighbor}$-nearest neighbors
    ($\glssymbol{kNearestNeighbor}$-NN) is based on the euclidean distance.},
    % 
    symbol={\kNearestNeighbor}
}

\newglossaryentry{edgeInclusionValue}
{
    name={\edgeInclusionValue},
    longform={edgeInclusionValue},
    capitalform={edgeInclusionValue},
    sort={wfcpEdgeInclusionValue},
    type={model},
    % 
    description={ The~\glssymbol{edgeInclusionValue} is a scaling factor that is
    used in the case when a new generated point violates the minimum pairwise
    distance. Then the whole wind farm is scaled up by
    a~$\glssymbol{edgeInclusionValue}>0$.
    See~\cref{ch:wfcp:sec:benchmark-generator} for more information. },
    % 
    symbol={\edgeInclusionValue}
}

\newglossaryentry{thermalConductivityCapacity}
{
    name={\thermalConductivityCapacity},
    longform={thermalConductivityCapacity},
    capitalform={thermalConductivityCapacity},
    sort={wfcpThermalConductivityCapacity},
    type={model},
    parent={temperature},
    % 
    description={The thermal conductivity and capacity is represented by the
    factor~$\glssymbol{thermalConductivityCapacity}$ that has influence on the
    temperature's drop~\glssymbol{temperature}. 
    },
    % 
    symbol={\thermalConductivityCapacity}
}

\newglossaryentry{windfarmTotalcost}
{
    name={\ensuremath{\totalcost}},
    longform={total cost},
    capitalform={Total Cost},
    sort={wfcpTotalcost},
    type={model},
    % 
    description={ The total cost~\glssymbol{windfarmTotalcost} is defined by the
    costs of the transport and export cables and is defined in~\cref{ch:wfcp:eq:total-cost-FFP-free-substation-positioning}. },
    % 
    symbol={\ensuremath{\totalcost}}
}

\newglossaryentry{windfarmCableCost}
{
    name={\ensuremath{\cost}},
    longform={windfarmCost},
    capitalform={windfarmCost},
    sort={wfcpCableCost},
    parent={windfarmTotalcost},
    type={model},
    % 
    description={ A cable type is among other things defined by its cost. The
    cost function is defined by~$\glssymbol{windfarmCableCost}\colon
    \glssymbol{cabletypes}\to\posreals$ and is non-convex.
    },
    % 
    symbol={\ensuremath{\cost}}
}

\newglossaryentry{windfarmSubstationCost}
{
    name={\ensuremath{\costsubstation}},
    longform={substation fixed costs},
    capitalform={Substation Fixed Costs},
    sort={wfcpCostsubstation},
    parent={windfarmTotalcost},
    type={model},
    % 
    description={
    The fixed costs for laying an export cable and for placing a
    substation are denoted by~$\glssymbol{windfarmSubstationCost}$.
    },
    % 
    symbol={\ensuremath{\costsubstation}}
}

\newglossaryentry{cuts}
{
    name={\ensuremath{ \cuts }},
    sort={wfcpCuts},
    type={model},
    % 
    description={ The edge cut~\glssymbol{cuts} is a set of edges~$
        \glssymbol{undirectededges}'\subsetneq
        \glssymbol{undirectededges}$ such that~$\glssymbol{graph}' = 
        \glssymbol{graph} - \glssymbol{undirectededges}'$. 
        % 
    },
    symbol={\ensuremath{ \cuts }}
}
